Synthesizing Symmetric Lenses

### 2018-07-03 papers/SymmetricLenses/main.tex
merge cherry-pick

\subsection{Benchmark Suite}
Our benchmarks are drawn from four different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In adopting
  these benchmarks, we go beyond the data cleaning tasks\bcp{confusing: you
    say these are data cleaning tasks, then immediately say we go beyond
    data cleaning tasks.  (I know the next bit of the sentence makes it
    (somewhat) clearer, but the reader is already lost right here.)}, and
  synthesize 
  synchronization functions\bcp{what is a ``synchronization function''}
  between the ad-hoc data and their cleaned forms. 
  Optician also adopted benchmarks from Flash Fill, but required alterations to
  be in bijective form\bcp{Mysterious}. With our symmetric enhancement, we
  \bcp{words missing?} Optician's four 
  benchmarks and 4 new Flash Fill benchmarks with no alterations.
\item We adapted \afm{29} benchmarks from Augeas.  These benchmarks are the same
  as those present in Optician.  While these benchmarks had to be slightly
  adopted for bijectivity, previous work addressed this lack of bijectivity by
  synthesizing quotient bijective lenses~\cite{?}.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{ Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete most of the benchmarks without using compositional
    synthesis. \bcp{The interesting part of the graph is all squished
      against the Y axis.  Can we make the X axis logarithmic?}}
  \label{fig:times}
\end{figure}

@@

\subsection{Symmetric Lenses}
\paragraph*{Formalization} We have reformulated the problem addressed by
symmetric lenses with simple symmetric lenses. Classically, these types of
synchronization tasks are represented as symmetric lenses. A symmetric lens
$\Lens$ between $X$ and $Y$ consists of 4 components: a complement $C$, a
designated element $init \in C$, and two functions for propagating changes in
each format to the other:
\begin{enumerate}
\item $\PutRSym \OfType X \times C \rightarrow Y \times C$
\item $\PutLSym \OfType Y \times C \rightarrow X \times C$
\end{enumerate}
In this formulation, the components of each format that aren't shared with the
other format are stored in the complement. When one format is edited, the \PutR
or \PutL function stitches together that edited data with the data for the other
side, stored in the complement.  The designated element, $init$, is used as the
initial value of $C$, and specifies default behavior when there isn't existing
data to stitch with.  In our example, the complement would consist of two lists
of commands, where one list contains the Linux commands and one list contains
the Windows commands.

@@

By describing our lenses in this complement style, we can express an incredibly
wide class of lenses, as these complements permit storing any amount of
information in them.  However, they pose problems when implementing them in
real-world systems and in synthesizing them.

\paragraph*{Issues with Symmetric Lenses} Using symmetric lenses for
synchronization forces us to maintain not just two files that we aim to
sycnrhonize, but three. This is unintuitive, and creates many problems in
practice. For example, consider the situation where I am synchronizing a crontab
and job manager file. I am synchronizing across computers, so I must either
maintain a copy of the complement on each computer, and keep them synchronized,
or figure out a computer to hold the complement, and make sure all edits go
through that complement. Furthermore, if I want to change the synchronization to
a different computer, I don't need to merely make sure that my files are moved
to the computer, I also have to make sure that I correctly move the complement,
and hook up that complement to be used for that synchronization task. This is a
huge divergence from other synchronization utilities, where all that needs to be
done is maintain the files. Using those for synchronization, edits can be sent
over the wire, and the appropriate function can stitch together those edits, no
additional state needed.

@@

@@

\begin{theorem}
  Let $\Lens$ be an asymmetric lens. $\Lens$ is also a simple symmetric lens,
  where
  \begin{center}
    \begin{tabular}{rcl}
      $\Lens.\CreateROf{x}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\CreateLOf{y}$ & $=$ & $\Lens.create \App y$\\
      $\Lens.\PutROf{x}{y}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\PutLOf{y}{x}$ & $=$ & $\Lens.put \App y \App x$
    \end{tabular}
  \end{center}
\end{theorem}

>>>>

\subsection{Benchmark Suite}
Our benchmarks are drawn from four different sources.\bcp{What makes this a good
  set of benchmarks for present purposes?}
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In adopting
  these benchmarks, we go beyond the data cleaning tasks\bcp{confusing: you
    say these are data cleaning tasks, then immediately say we go beyond
    data cleaning tasks.  (I know the next bit of the sentence makes it
    (somewhat) clearer, but the reader is already lost right here.)}, and
  synthesize 
  synchronization functions\bcp{what is a ``synchronization function''}
  between the ad-hoc data and their cleaned forms. 
  \bcp{Clarify:}Optician also adopted benchmarks from Flash Fill, but required alterations to
  be in bijective form\bcp{Mysterious}. With our symmetric enhancement, we
  \bcp{words missing?} Optician's four 
  benchmarks and 4 new Flash Fill benchmarks with no alterations.
\item We adapted \afm{29} benchmarks from Augeas.  These benchmarks are the same
  as those present in Optician.  \bcp{I (think I) understand what this
    means, but readers will not.}While these benchmarks had to be slightly
  adapted for bijectivity, previous work addressed this lack of bijectivity by
  synthesizing quotient bijective lenses~\cite{?}.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete most of the benchmarks without using compositional
    synthesis. \bcp{The interesting part of the graph is all squished
      against the Y axis.  Can we make the X axis logarithmic?}}
  \label{fig:times}
\end{figure}

@@

\subsection{Symmetric Lenses}
\bcp{I suggest adding an adjective---e.g., ``classic symmetric lenses''---to
avoid confusion between the old ones and our new ones.}
\paragraph*{Formalization} We have reformulated the problem addressed by
symmetric lenses with simple symmetric lenses. Classically, these types of
synchronization tasks are represented as symmetric lenses. A symmetric lens
$\Lens$ between $X$ and $Y$ consists of 4 components: a complement $C$, a
designated element $init \in C$, and two functions for propagating changes in
each format to the other:
\begin{enumerate}
\item $\PutRSym \OfType X \times C \rightarrow Y \times C$
\item $\PutLSym \OfType Y \times C \rightarrow X \times C$
\end{enumerate}
In this formulation, the components of each format that aren't shared with the
other format are stored in the complement. When one format is edited, the \PutR
or \PutL function stitches together that edited data with the data for the other
side, stored in the complement.  The designated element, $init$, is used as the
initial value of $C$, and specifies default behavior when there isn't existing
data to stitch with.  In our example\bcp{which example?}, the complement
would consist of two lists 
of commands, where one list contains the Linux commands and one list contains
the Windows commands.

@@

By describing our lenses in this complement style, we can express an incredibly
wide class\bcp{where is the evidence that this class of lenses is {\em
    usefully} wider than simple symmetric lenses?} of lenses, as these complements permit storing any amount of
information in them.  However, they pose problems when implementing them in
real-world systems and in synthesizing them.

\paragraph*{Issues with Symmetric Lenses} Using symmetric lenses for
synchronization forces us to maintain not just two files that we aim to
sycnrhonize, but three. \bcp{I don't find it unintuitive, and I think we
  should be careful not to oversell the difficulty of storing the
  complements.  It requires more engineering, but it's not rocket
  science.}This is unintuitive, and creates many problems in 
practice. For example, consider the situation where I am synchronizing a crontab
and job manager file. I am synchronizing across computers, so I must either
maintain a copy of the complement on each computer, and keep them synchronized,
or figure out a computer to hold the complement, and make sure all edits go
through that complement. Furthermore, if I want to change the synchronization to
a different computer, I don't need to merely make sure that my files are moved
to the computer, I also have to make sure that I correctly move the complement,
and hook up that complement to be used for that synchronization task. This is a
huge divergence from other synchronization utilities\bcp{No.  For example,
  Unison maintains a database on each replica recording, for each file, what
its hash was after the last time the two replicas were synchronized.}, where all
that needs to be 
done is maintain the files. Using those for synchronization, edits can be sent
over the wire, and the appropriate function can stitch together those edits, no
additional state needed.

@@

\bcp{I guess we could also show that equivalence of simple symmetric lenses
  is just the identity relation?}

@@

\begin{theorem}\bcp{To prove this, we need to state the type and laws for
  asymmetric lenses.}
  Let $\Lens$ be an asymmetric lens. $\Lens$ is also a simple symmetric lens,
  where
  \begin{center}
    \begin{tabular}{rcl}
      $\Lens.\CreateROf{x}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\CreateLOf{y}$ & $=$ & $\Lens.create \App y$\\
      $\Lens.\PutROf{x}{y}$ & $=$ & $\Lens.get \App x$\\
      $\Lens.\PutLOf{y}{x}$ & $=$ & $\Lens.put \App y \App x$
    \end{tabular}
  \end{center}
\end{theorem}
